Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-05 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
completion of AUDPC calculations and edits to ensure the correct data is upgraded

# COULD NOT GET TO MATCH
# insert new calculations into data
# #PM_MB_means <- 
#    replace_data(template_data = PM_MB_means, 
#                             new_data = Herm_17_m, 
#                             new_data_column = "AUDPC_m", 
#                             ignore_columns = c(4,5,7,8,10:16,29:46))
# 
# PM_MB_means <- replace_data(template_data = PM_MB_means,
#                             new_data = Herm_17_m,
#                             new_data_column = "AUDPC_sd",
#                             ignore_columns = c(5:8,10:16,29:46))

Herm_17_m
PM_MB_means[PM_MB_means$trial_ref == "mung1617/01",]

colnames(PM_MB_means)

@@

>>>>

# COULD NOT GET TO MATCH
# insert new calculations into data
# #PM_MB_means <- 
   # replace_data(template_data = PM_MB_means,
   #                          new_data = Herm_17_m,
   #                          new_data_column = "AUDPC_m",
   #                          ignore_columns = c(4,5,7,8,10:16,29:46))

# PM_MB_means <- replace_data(template_data = PM_MB_means,
#                             new_data = Herm_17_m,
#                             new_data_column = "AUDPC_sd",
#                             ignore_columns = c(5:8,10:16,29:46))

@@

```{r Save_PM_MB_means}

write.csv(PM_MB_means, file = "/data/PM_MB_updated.csv")
